### 2011-11-04 doc/pldi2012/highlevel.tex

\begin{center}
\begin{table}
\begin{tabular}{|c|c|c|c|c|} \hline
             & Exclusive & Atomic   & Simultaneous & Relaxed \\ \hline 
Exclusive    & Conflict  & Conflict & Conflict     & Conflict \\ \hline
Atomic       & Conflict  & Same Instance & Contingent & Contingent \\ \hline
Simultaneous & Conflict  & Contingent & Same Instance & None \\ \hline
Relaxed      & Conflict  & Contingent & None & None \\ \hline
\end{tabular}
\caption{Conflict detection cases when at least one access is a write.\label{tab:conflicts}}
\end{table}
\end{center}
In this table, {\em Conflict} indicates that there will always be a conflict between
regions while {\em None} indicates that there will never be a conflict regardless
of mapping decisions.  In the case of {\em Same Instance} there is a conflict contingent
upon a mapping decision.  If both tasks map to the same physical instance (described in 
more detail in section \ref{subsec:instmang}) then there is no conflict, which if
they map to different instances there is a conflict as the system will have to generate
a copy between the two tasks running.

For the case of {\tt Contingent} there are two special cases that we handle.
One special case is Write-After-Read (WAR) conflicts.  For the WAR case, if neither coherence property
is {\em Exclusive} then we can ensure that different physical instances
are used to avoid a conflict and increase parallelism.  If either property is {\em Exclusive} then the semantics
of the programming model mandate that we detect a conflict and serialize the task.

Another special case occurs if there is an {\tt Atomic} writer and either {\tt Simultaneous}
or {\tt Relaxed} reader.  In this case it is acceptable for the tasks to run in
parallel as it is valid for the reader to see updates form the writer, and the
reader will not violate the atomic access semantics of the writer.

@@

\subsubsection{Instance Management}
\label{subsec:instmang}

>>>>

\begin{center}
\begin{table}
\begin{tabular}{|c|c|c|c|c|} \hline
             & Exclusive & Atomic   & Simultaneous & Relaxed \\ \hline 
Exclusive    & Conflict  & Conflict & Conflict     & Conflict \\ \hline
Atomic       & Conflict  & Same Instance & Conflict & Conflict \\ \hline
Simultaneous & Conflict  & Conflict & Same Instance & None \\ \hline
Relaxed      & Conflict  & Conflict & None & None \\ \hline
\end{tabular}
\caption{Conflict detection cases}
\end{table}
\end{center}

@@

\subsubsection{Instance Management}
